---
title: "Bears Analysis"
format: 
  html:
    toc: true
    theme: flatly
    self-contained: true
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3
)

# Load libraries
library(tidyverse)
library(here)

# Read in data 
bears <- read_csv(here::here('data', 'bear_killings.csv'))
```

### Which months have the highest frequency of bear killings?

```{r}
bears %>% 
  count(month) %>% 
  arrange(desc(n))
```

Most attacks occur during the **summer**, with August having the highest number of attacks.

### Who has been killed more often by bears: hunters or hikers?

```{r}
bears %>% 
  count(hunter, hiker)
```

Although *hunters* are killed more often than *hikers*, the vast majority of the data set does not record the hunter / hiker status of the victims. 

### How do the the number of bear attacks on men vs women compare?

```{r}
bears %>% 
  count(gender)
```

Far more attacks have involved men than women. 
