---
title: "Power Analysis"
format: html
theme: united
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3
)

library(tidyverse)
library(cbcTools)
```

First, define the attributes and levels:

```{r}
profiles <- cbc_profiles(
  price       = c(15, 20, 25), # Price ($1,000)
  fuelEconomy = c(20, 25, 30), # Fuel economy (mpg)
  accelTime   = c(6, 7, 8),    # 0-60 mph acceleration time (s)
  powertrain  = c('Gasoline', 'Electric')
)
```

# Random design

Make a randomized full-factorial design:

```{r}
design_rand <- cbc_design(
  profiles = profiles,
  n_resp   = 500, # Number of respondents
  n_alts   = 3,   # Number of alternatives per question
  n_q      = 6    # Number of questions per respondent
)

head(design_rand)

cbc_balance(design_rand)
cbc_overlap(design_rand)
```

Simulate random choices

```{r}
data_rand <- cbc_choices(
    design = design_rand,
    obsID = "obsID"
)
```

Run power analysis

```{r}
power_rand <- cbc_power(
    nbreaks = 10,
    n_q     = 6,
    data    = data_rand,
    pars    = c("price", "fuelEconomy", "accelTime", "powertrain"),
    outcome = "choice",
    obsID   = "obsID"
)

head(power_rand)
tail(power_rand)
```

Here is a summary of the standard errors for each sample size:

```{r}
ggplot(power_rand) +
  geom_hline(yintercept = 0.05, color = "red", linetype = 2) +
  geom_point(aes(x = sampleSize, y = se, color = coef)) +
  expand_limits(y = 0) +
  scale_y_continuous(limits = c(0, 0.125)) +
  theme_bw() + 
  labs(
    x = "Sample size", 
    y = "Standard error", 
    color = "Coefficient"
  )
```



# Bayesian D-efficient design

Make a Bayesian D-efficient fractional factorial design:

```{r}
priors <- list(
  price       = -0.1,
  fuelEconomy = 0.1,
  accelTime   = -0.1,
  powertrain  = -4
)

design_db_eff <- cbc_design(
  profiles  = profiles,
  n_resp    = 500, # Number of respondents
  n_alts    = 3,   # Number of alternatives per question
  n_q       = 6,   # Number of questions per respondent
  n_start   = 10, 
  n_blocks  = 1,
  priors = priors
)

head(design_db_eff)
```

Simulate choices

```{r}
data_db_eff <- cbc_choices(
    design = design_db_eff,
    obsID  = "obsID",
    priors = priors
)

head(data_db_eff)

cbc_balance(design_db_eff)
cbc_overlap(design_db_eff)
```

Run power analysis

```{r}
power_db_eff <- cbc_power(
    nbreaks = 10,
    n_q     = 6,
    data    = data_db_eff,
    pars    = c("price", "fuelEconomy", "accelTime", "powertrain"),
    outcome = "choice",
    obsID   = "obsID"
)

head(power_db_eff)
tail(power_db_eff)
```

Here is a summary of the standard errors for each sample size:

```{r}
ggplot(power_db_eff) +
  geom_hline(yintercept = 0.05, color = "red", linetype = 2) +
  geom_point(aes(x = sampleSize, y = se, color = coef)) +
  expand_limits(y = 0) +
  scale_y_continuous(limits = c(0, 0.125)) +
  theme_bw() + 
  labs(
    x = "Sample size", 
    y = "Standard error", 
    color = "Coefficient"
  )
```

