---
title: "Pilot Survey"
toc: true
toc-location: right
execute:
  echo: false
  warning: false
  message: false
params:
  number: 3
  weight: '5%'
---

```{r}
#| label: setup

source(here::here("_common.R"))

rubric <- read_csv(here::here('rubrics', '3-pilot-survey.csv'))
maxPoints <- rubric %>%
    filter(rating == "Excellent") %>%
    summarise(max = sum(maxPoints)) %>%
    pull(max)
```

```{r child = here::here("fragments", "project.qmd")}
```

As a team, create a **pilot survey** - an initial draft of your final survey for preliminary testing. Your fellow classmates will all take your survey and provide feedback. The course instructor will also review and grade your survey and will provide written feedback. Follow the instructions below to prepare your pilot survey.

# 1. Get Organized

Download and unzip the [demo choice-based conjoint survey](https://github.com/surveydown-dev/demo-choice-based-conjoint/archive/refs/heads/main.zip) for your pilot survey. The folder contains the following files:

- `survey.Rproj`: An R Project file for staying organized.
- `make-choice-questions.R`: The code to generate the `choice_questions.csv` file (your survey design file...use the code you wrote in class for this).
- `choice_questions.csv`: The survey choice question design file.
- `survey.qmd`: The code for creating your survey content, which should include a welcome page, content form, and eligibility questions for screening our ineligible respondents. It should also include your education content and randomized conjoint choice questions, then any other questions you wish to ask your survey respondents (e.g. demographics).
- `app.R`: The file to run the Shiny app.
- `images`: A folder of images (if you're using any in your survey). 

# 2. Write your survey content

The files included in the zip file are just example content based on the [blog post](https://surveydown.org/blog/2024-08-28-choice-based-conjoint-surveys-with-surveydown/) on building conjoint surveys in surveydown. **This is just placeholder content - you need to replace it with your survey content**.

Follow these guidelines in inserting your content:

- You may directly copy and paste any content you wish from your [Survey Plan](https://madd.seas.gwu.edu/2024-Fall/project/2-survey-plan.html) assignment.
- In your `survey.qmd` file, you should have your randomized sets of choice questions working using your `choice_questions.csv` design file.
- Setup a [database connection](https://surveydown.org/store-data) on Supabase and make sure your survey data is being stored properly in the database.

> Be sure to render your `survey.qmd` file often to an html file so you can preview that everything is displaying as expected, then also run the `app.R` file to preview your choice questions locally as a Shiny app.

# 3. Upload your survey to shinyapps.io

Only one person from your team should create an account for hosting your survey on shinyapps.io. Follow the documentation on [deploying the app](https://surveydown.org/deployment).

# 4. Attribution

Include a short description of the specific contributions of each team member for this report. If all members contributed equally, you can just put the single sentence "All members contributed equally".

Team members who do not make meaningful contributions to their projects will not receive the same grade as that of their team mates. If you are having any issues or disputes among team members, please contact Professor Helveston ASAP so we can find a resolution.

# 5. Submit

Create a zip file of all the files in your R project folder for this assignment and submit it on the corresponding assignment submission on Blackboard. **Only one person from your team should submit the report.**

# Grading Rubric

**`r maxPoints` Total Points**

```{r, echo=FALSE}
make_rubric(rubric)
```
